Very simplified likelihood

### 2024-02-21 inst/very_simplified_likelihood.Rmd
other bugfix

plot(NA,xlim=c(0,1),ylim=c(0,1),type='n')
M <- cbind(a=a,b=1-a)
for(r in 0:7){
  y <- loglik(M,fhyper3(r,n),log=FALSE)
  y <- y/max(y, na.rm=TRUE)
points(M[,2],y,type="l",lwd=8)
}
```

>>>>

plot(NA,xlim=c(0,1),ylim=c(0,1),type='n')
M <- cbind(a=a,b=1-a)
for(r in 0:7){
  y <- loglik(M,fhyper3(r,n),log=FALSE)
  y <- y/max(y, na.rm=TRUE)
points(M[,1],y,type="l",lwd=8)
}
```
